---
title: "Homework 6"
author: "Jacob Townsley"
date: "3/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1 Cleaning Missing Values
```{r}
setwd('/Users/jacobtownsley/Desktop')
HAPPY <- readRDS("data/HAPPY.rds")
HAPPY[HAPPY == "IAP"] = NA
HAPPY[HAPPY == "DK"] = NA
HAPPY[HAPPY == "NA"] = NA
```

# Part 1 HAPPY
```{r}
HAPPY[HAPPY == '89 OR OLDER'] = '89'
HAPPY$AGE = as.numeric(HAPPY$AGE)
```

# Part 1 AGE
```{r}
HAPPY$HAPPY = as.factor(HAPPY$HAPPY)
```

# Part 1 SEX
```{r}
HAPPY$SEX = as.factor(HAPPY$SEX)
```

# Part 1 MARITAL
```{r}
HAPPY$MARITAL = as.factor(HAPPY$MARITAL)
HAPPY$MARITAL = factor(HAPPY$MARITAL, levels = c("MARRIED", "DIVORCED", "SEPARATED", "WIDOWED", "NEVER MARRIED"))
```

# Part 1 DEGREE
```{r}
HAPPY$DEGREE = as.factor(HAPPY$DEGREE)
HAPPY$DEGREE = factor(HAPPY$DEGREE, levels = c("LT HIGH SCHOOL", "HIGH SCHOOL", "JUNIOR COLLEGE", "BACHELOR", "GRADUATE"))
```

# Part 1 FINRELA
```{r}
HAPPY$FINRELA = as.factor(HAPPY$FINRELA)
HAPPY$FINRELA = factor(HAPPY$FINRELA, levels = c("FAR BELOW AVERAGE", "BELOW AVERAGE", "AVERAGE", "ABOVE AVERAGE", "FAR ABOVE AVERAGE"))
```

# Part 1 HEALTH
```{r}
HAPPY$HEALTH = as.factor(HAPPY$HEALTH)
HAPPY$HEALTH = factor(HAPPY$HEALTH, levels = c("POOR", "FAIR", "GOOD", "EXCELLENT"))
```

# Part 1 PARTYID
```{r}
HAPPY$PARTYID = as.factor(HAPPY$PARTYID)
HAPPY$PARTYID = factor(HAPPY$PARTYID, levels = c("STRONG DEMOCRAT", "NOT STR DEMOCRAT", "IND,NEAR DEM", "INDEPENDENT", "IND,NEAR REP", "NOT STR REPUBLICAN", "STRONG REPUBLICAN", "OTHER PARTY"))
```

# Part 1 POLVIEWS
```{r}
HAPPY$POLVIEWS = as.factor(HAPPY$POLVIEWS)
HAPPY$POLVIEWS = factor(HAPPY$POLVIEWS, levels = c("EXTREMELY LIBERAL", "LIBERAL", "SLIGHTLY LIBERAL", "MODERATE", "SLIGHTLY CONSERVATIVE", "CONSERVATIVE", "EXTREMELY CONSERVATIVE"))
```

# Part 1 Saving Final Data Set
```{r}
setwd('/Users/jacobtownsley/Desktop')
saveRDS(HAPPY, 'data/HAPPY.rds')
```

# Part 2 Individual Exploration (Jacob)

## How does health and sex influence happiness?
```{r}
library(ggplot2)
ggplot(data = HAPPY, aes(x = HEALTH, y = HAPPY, color = SEX)) + geom_count()
```

This graph shows that better health (good and excellent) is associated with higher levels in happiness (pretty happy and very happy) in many cases. There does not seem to be a major change between females and males for any of the categories. More evidence for this should be sought because there are many missing values for health in this data set.

I worked alone on this project. The GitHub repository I posted to is "practice1-jtownsley25". The link for this is https://github.com/jtownsley25/practice1-jtownsley25.





